Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-14 paper/paper.tex
remiving unneeded section header

\section{Recovering a Perfect Partition}
\label{sec:ppl}
\subsection{Perfect Partition Model}\label{sec:perfectPartition}
\maciek{Here introduce a restricted model of \PPOBRP{}, the restricted variant where the input sequence can be perfectly partitioned}
\maciek{ every algorithm must colocate every communicating pair.
	\mahmoud{updated!}}
In this paper we mostly focus on a restricted variant of   \PPOBRP{}
where the communication graph can be partitioned into $\ell$ clusters without any inter-cluster edges.
Moreover, we assume an optimal offline algorithm (OPT) moves to this \emph{perfect partition}
at the beginning and stays there permanently.
Then the task of an online algorithm is to "recover" (or learn) the perfect partition while not paying too much more than OPT.
This implies that on a request between any two non-collocated nodes,
any online algorithm must eventually collocate them,
as otherwise it not competitive under a sequence that repeats the same request arbitrarily many times.

>>>>

\section{Recovering a Perfect Partition}	\label{sec:ppl}
%\subsection{Perfect Partition Model}\label{sec:perfectPartition}
\maciek{Here introduce a restricted model of \PPOBRP{}, the restricted variant where the input sequence can be perfectly partitioned}
\maciek{ every algorithm must colocate every communicating pair.
	\mahmoud{updated!}}
We  focus on a restricted variant of   \PPOBRP{}
where the communication graph can be partitioned into $\ell$ clusters without any inter-cluster edges.
Moreover, we assume an optimal offline algorithm (OPT) moves to this \emph{perfect partition}
at the beginning and stays there permanently.
Then the task of an online algorithm is to "recover" (or learn) the perfect partition while not paying too much more than OPT.
This implies that on a request between any two non-collocated nodes,
any online algorithm must eventually collocate them,
as otherwise it not competitive under a sequence that repeats the same request arbitrarily many times.
